An asymptotically normal out-of-sample test of equal predictive accuracy for nested models

### 2012-06-28 Paper.tex
Changed margins and formatting to improve editability
Minor change to 'thanks' section

\documentclass[12pt,fleqn]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round,comma]{natbib}
\usepackage[top=1.25in,left=1.25in,right=1.25in,bottom=1.25in]{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing\onehalfspacing
\input{tex/simulationdefinitions}
\input{tex/empiricsdefinitions}
\input{tex/empiricalresults}

@@

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}.  Web:
    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting for helpful comments.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    \textsc{rfs} paper with Ivo
    Welch \citep{GoW:08}.} \\
  Iowa State University}

@@

\date{\input{VERSION% <- allows VERSION to have comments
}}
\maketitle

@@

\newpage

@@

\begin{table}[tb]
  \centering
  \input{floats/simulation1}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; and Pr[disagree]
    gives the fraction of simulations in which this paper's test and
    Clark and West's (2007) give different conclusions.}
\label{tab:mc1}
\end{table}

@@

\begin{table}[tb]
  \centering
  \input{floats/simulation2}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; Pr[disagree] gives
    the fraction of simulations in which this paper's test and Clark and
    West's (2007) give different conclusions.}
\label{tab:mc2}
\end{table}

@@

\bibliography{AllRefs}
\end{document}

>>>>

\documentclass[11pt,fleqn]{article}

\usepackage{amsfonts}
\usepackage{amsmath,amsthm,amssymb,graphicx,setspace,url,booktabs,tabularx,enumerate,slantsc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage[nolists,nomarkers]{endfloat}
\usepackage[sort,round,comma]{natbib}
\usepackage{geometry}
\usepackage[small]{caption}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\bibliographystyle{abbrvnat}
\newcommand\citepos[2][]{\citeauthor{#2}'s \citeyearpar[#1]{#2}}
\newcommand\poscw{\citeauthor{ClW:06}'s \citeyearpar{ClW:06,ClW:07}}
\newcommand\citen[1]{\citeauthor{#1}, \citeyear{#1}}
\frenchspacing
\input{tex/mcDef}
\input{tex/ap}

@@

\author{Gray Calhoun\thanks{ Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \texttt{gcalhoun@iastate.edu}.  Web:
    \texttt{http://www.econ.iastate.edu/$\sim$gcalhoun}.  I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Allan Timmermann, Stephane
    Meng-Feng Yen and participants at the 2011 Midwest Econometrics
    Group meeting for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    \textsc{rfs} paper with Ivo
    Welch \citep{GoW:08}.} \\
  Iowa State University}

@@

\date{December 9, 2011}

\maketitle

@@

\newpage 
\newgeometry{top=1.2222in,left=0.9444in,right=1.8889in,bottom=2.4444in}

@@

\begin{table}[tb]
  \centering
  \input{tex/mc1}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp1} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; and Pr[disagree]
    gives the fraction of simulations in which this paper's test and
    Clark and West's (2007) give different conclusions.}
\label{tab:mc1}
\end{table}

@@

\begin{table}[tb]
  \centering
  \input{tex/mc2}
  \caption{Size and power of the \oos\ tests under \eqref{eq:dgp2} at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\textsc{cw}] shows the fraction of simulations for which Clark
    and West's (2007) statistic rejects; Pr[new] shows the fraction of
    simulations for which this paper's test rejects; Pr[disagree] gives
    the fraction of simulations in which this paper's test and Clark and
    West's (2007) give different conclusions.}
\label{tab:mc2}
\end{table}

@@

\bibliography{texextra/AllRefs}
\end{document}
